\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-19 evaluation.tex
minor changes

We performed all experiments using the Windows PowerShell tool on a 2.50GHz Intel Core i5-4300U CPU with 8GB RAM running Windows 10 Pro 64-bit. We configured the engine to perform 100,000 iterations. The random seed for both schedulers was generated in each iteration using the \texttt{DateTime.Now.Millisecond} API which returns the current time in milliseconds. The PCT scheduler was further configured with a bug depth of 2 and a max number of scheduling steps of 500. All reported times are in seconds.

@@

For the MigratingTable case study, the first 7 bugs in Table~\ref{tab:testing} were discovered using a \psharp test harness based on nondeterministically generated, but controlled by \psharp, input history. For each of these found bugs, we manually reviewed one of the bug traces to confirm if it reflected the expected bug. The remaining 4 bugs (denoted with $\diamond$) are known bugs that we were unable to find with the fully-randomized test harness in the 100,000 iterations. We believe this is due to unlucky random choices of inputs and schedules by the \psharp systematic testing engine. We wrote a custom \psharp test harness for each of these bugs, which allowed \psharp to quickly reproduce them. Note that using a custom test harness does not represent a testing method one could use to find unknown bugs in software. However, in this case the objective was to simply reproduce these known bugs.

The QueryStreamedBackUpNewStream bug in MigratingTable, that was found using \psharp, stands out because it reflects the type of oversight that tends to occur as designs evolve. We will not discuss the details of the bug due to space constraints, but \psharp managed to discover this bug in a matter of seconds. The MigratingTable developers spent about 10 minutes analyzing the trace to diagnose what was happening; granted, this was after days of experience analyzing traces. The developers had to extend the logging of \psharp with additional trace information to understand the bug. This is expected since \psharp only outputs trace information related to its communicating state machines. The trace information can be easily extended though; this was done in all our case studies.

>>>>

We performed all experiments using the Windows PowerShell tool on a 2.50GHz Intel Core i5-4300U CPU with 8GB RAM running Windows 10 Pro 64-bit. We configured the engine to perform 100,000 iterations. The random seed for both schedulers was generated using the current time. The PCT scheduler was further configured with a bug depth of 2 and a max number of scheduling steps of 500. All reported times are in seconds.

@@

For the MigratingTable case study, the first 7 bugs in Table~\ref{tab:testing} were discovered using a \psharp test harness based on nondeterministically generated, but controlled by \psharp, input history. For each of these found bugs, we manually reviewed one of the bug traces to confirm if it reflected the expected bug. The remaining 4 bugs (denoted with $\diamond$) are known bugs that we were unable to find with the fully-randomized test harness in the 100,000 iterations. We believe this is due to unlucky random choices of inputs and schedules by the \psharp testing engine. We wrote a custom \psharp test harness for each of these bugs, which allowed \psharp to quickly reproduce them. Note that using a custom test harness does not represent a testing method one could use to find unknown bugs in software. However, in this case the objective was to simply reproduce these known bugs.

The QueryStreamedBackUpNewStream bug in MigratingTable, that was found using \psharp, stands out because it reflects the type of oversight that tends to occur as designs evolve. We do not discuss the details of the bug due to space constraints, but \psharp managed to discover this bug in a matter of seconds. The MigratingTable developers spent just 10 minutes analyzing the trace to diagnose what was happening; although, this was after days of experience analyzing traces. The developers extended the logging of \psharp with additional trace information to understand the bug. \psharp only outputs trace information related to its communicating state machines, but the trace information is easy to extend and was done in all our case studies.
